Quantitative Benchmarking for Automatically Generated Conjectures

### 2017-11-23 TEBenchmarkPaper/article.tex
Use matplotlib and seaborn to draw graphs
Add caption to time plot

\begin{figure}
  \includegraphics[width=8cm]{graphs/time}
  \includegraphics[width=8cm]{graphs/precRec}
  \caption{}
  \label{figure:quickspec_results}
\end{figure}

>>>>

\begin{figure}
  \centering
  \input{time.pgf}
  \caption{Running times of QuickSpec on theories sampled from TIP. Each point
    is an individual run, with 30 per size except for 1 (14) and 2 (29). Colour
    indicates the total number of conjectures produced by each run, with failing
    processes shown in red. Some points are shifted horizontally to prevent
    overlaps. Standard box plots are included, although many are obscured due to
    quartiles near zero or timeout.}
  \label{figure:quickspec_results}
\end{figure}

\begin{figure}
  \centering
  \input{prec.pgf}
  \caption{}
  \label{figure:quickspec_results}
\end{figure}
